### 2018-06-28 Manuscripts/cog-psych/revision/methods_results_e3.tex
Likelihood ratio tests for correlation might not be appropriate. Until I find a better solution, run bootstraps first.

Experiment 2 recruited 122 participants who each generated one set of four Alpha
and four Beta category exemplars. Among these 122 generated category sets were
102 unique sets (i.e., they contained a unique collection of Alpha and Beta
exemplars). Consequently, for Experiment 3, we recruited 102 participants with
one participant presented with a different unique category set.

@@

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.

>>>>

Experiment 2 recruited 122 participants who each generated one set of four Alpha
and four Beta category exemplars. Experiment 3 recruited the same number of
participants.

@@

Among the 122 originally generated category sets were 102 unique sets (i.e.,
they contained a unique collection of Alpha and Beta exemplars). Consequently,
for our subsequent analyses for this experiment we only use data from the first
102 participants that were presented with a unique category set.

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$; min max?). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.
